---
title: "lab_report_knapsack"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{lab_report_knapsack}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
## Import
```{r setup}
library(lab6package)
```

## Brute force search
```{r}
system.time(brute_force_knapsack(x = knapsack_objects[1:16,], W = 3500))
```
## Dynamic programming
```{r}
system.time(knapsack_dynamic(x = knapsack_objects[1:500,], W = 3500))
```
## Greedy heuristic
```{r}
RNGversion(min(as.character(getRversion()),"3.5.3"))
set.seed(42, kind = "Mersenne-Twister", normal.kind = "Inversion")
n <- 1000000
knapsack_objects_2 <- data.frame(
                      w=sample(1:4000, size = n, replace = TRUE),
                      v=runif(n = n, 0, 10000)
                      )

system.time(greedy_knapsack(x = knapsack_objects_2[1:1000000,], W = 3500))
```
## Profile and optimize the code
In *Brute force search* function, we used two for-loops to enumerate all the potential combinations and to extract from the original data frame at the very beginning. Then we found that it costs too much time so decided to change to use **intToBits()**. Thus, a lot of time saved.

## Implentation in Rcpp
When we use **profvis** to examine *Brute force search* function, we found the most time-consuming part is the for-loop that goes through all the combinations. So we created a cpp function to replace it if argument *fast* sets as TRUE. The speed boost is obvious.
```{r}
system.time(brute_force_knapsack(x = knapsack_objects[1:20,], W = 3500))
system.time(brute_force_knapsack(x = knapsack_objects[1:20,], W = 3500, fast = TRUE))
```

